---
title: "Analysis of within/between correlations"
output: html_notebook
---

```{r}
require(plyr)
require(tidyverse)
require(bootES)
require(stringr)
require(broom)
```

# First we look at hyperaligned data
```{r, message=FALSE, warning=FALSE}
fns <- Sys.glob('*hpal*correlations.csv')
systems <- c('Anterior Core', 'Core', 'Dorsal Core',
             'Extended', 'Precuneus', 'Theory of Mind', 'Ventral Core')
load_csv <- function(csv) {
  df <- read_csv(csv)
  df$system <- mapvalues(csv, fns, systems)
  return(df)
}

df <- ldply(fns, load_csv)
df <-
df %>%
  group_by(system) %>%
  mutate(diff=within-between, mdiff=mean(diff))

df$system <-
  factor(df$system,
         levels=c('Core', 'Ventral Core', 'Dorsal Core', 
                  'Anterior Core', 'Extended', 'Precuneus', 'Theory of Mind'))

df_general <- df %>%
  filter(system %in% c('Core', 'Extended'))

df_within_core <- df %>%
  filter(system %in% c('Ventral Core', 'Dorsal Core', 'Anterior Core'))
df_within_ext <- df %>%
  filter(system %in% c('Precuneus', 'Theory of Mind'))

```

## Plot within core and within extended
```{r}
ggplot(df_general, aes(system, diff)) + 
  geom_point(position=position_jitter(w=0.2),
             size=1, alpha=0.8) +
  geom_crossbar(aes(ymin=mdiff, ymax=mdiff, y=mdiff),
                fatten=2.5, width=0.4) +
  theme_bw() +
  labs(x='System', y='Within - Between Correlation') +
  coord_cartesian(ylim=c(0, 0.25))# +
  #theme(axis.text.x=element_text(angle=0, hjust=0))

ggsave('hpal_core_ext.pdf', width=8, height=6)
```

## Plot the distinctions within the core system  
```{r}
ggplot(df_within_core, aes(system, diff)) + 
  geom_point(position=position_jitter(w=0.2),
             size=1, alpha=0.8) +
  geom_crossbar(aes(ymin=mdiff, ymax=mdiff, y=mdiff),
                fatten=2.5, width=0.4) +
  theme_bw() +
  labs(x='System', y='Within - Between Correlation') +
  coord_cartesian(ylim=c(0, 0.5))# +
  #theme(axis.text.x=element_text(angle=0, hjust=0))
ggsave('hpal_core.pdf', width=8, height=6)
```

## Plot the distinctions between the extend system
```{r}
ggplot(df_within_ext, aes(system, diff)) + 
  geom_point(position=position_jitter(w=0.2),
             size=1, alpha=0.8) +
  geom_crossbar(aes(ymin=mdiff, ymax=mdiff, y=mdiff),
                fatten=2.5, width=0.4) +
  theme_bw() +
  labs(x='System', y='Within - Between Correlation') +
  coord_cartesian(ylim=c(0, 0.3))# +
  #theme(axis.text.x=element_text(angle=0, hjust=0))
ggsave('hpal_ext.pdf', width=8, height=6)
```

## Compute bootstrapped CIs

```{r, message=FALSE, warning=FALSE}
get_ci <- function(x, R=100) {
  ci <- bootES(x, R=R)
  return(data.frame(t0=ci$t0, lci=ci$bounds[1], rci=ci$bound[2]))
}

# set seed for reproducibility
set.seed(7)
cis <-
df %>%
  group_by(system) %>%
  do(get_ci(.$diff, R=10000))

cis <- 
df %>%
  group_by(system) %>%
  summarise(within=mean(within), between=mean(between)) %>%
  merge(cis)

cis
```

# Next we look at task data
```{r, message=FALSE, warning=FALSE}
fns <- Sys.glob('*task*correlations.csv')
systems <- c('Anterior Core', 'Core', 'Dorsal Core',
             'Extended', 'Precuneus', 'Theory of Mind', 'Ventral Core')
load_csv <- function(csv) {
  df <- read_csv(csv)
  df$system <- mapvalues(csv, fns, systems)
  return(df)
}

df <- ldply(fns, load_csv)
df <-
df %>%
  group_by(system) %>%
  mutate(diff=within-between, mdiff=mean(diff))

df$system <-
  factor(df$system,
         levels=c('Core', 'Ventral Core', 'Dorsal Core', 
                  'Anterior Core', 'Extended', 'Precuneus', 'Theory of Mind'))

df_general <- df %>%
  filter(system %in% c('Core', 'Extended'))

df_within_core <- df %>%
  filter(system %in% c('Ventral Core', 'Dorsal Core', 'Anterior Core'))
df_within_ext <- df %>%
  filter(system %in% c('Precuneus', 'Theory of Mind'))

```

## Plot within core and within extended
```{r}
ggplot(df_general, aes(system, diff)) + 
  geom_point(position=position_jitter(w=0.2),
             size=1, alpha=0.8) +
  geom_crossbar(aes(ymin=mdiff, ymax=mdiff, y=mdiff),
                fatten=2.5, width=0.4) +
  theme_bw() +
  labs(x='System', y='Within - Between Correlation') +
  #coord_cartesian(ylim=c(0, 0.25))# +
  #theme(axis.text.x=element_text(angle=0, hjust=0))

ggsave('task_core_ext.pdf', width=8, height=6)
```

## Plot the distinctions within the core system  
```{r}
ggplot(df_within_core, aes(system, diff)) + 
  geom_point(position=position_jitter(w=0.2),
             size=1, alpha=0.8) +
  geom_crossbar(aes(ymin=mdiff, ymax=mdiff, y=mdiff),
                fatten=2.5, width=0.4) +
  theme_bw() +
  labs(x='System', y='Within - Between Correlation') +
  #coord_cartesian(ylim=c(0, 0.5))# +
  #theme(axis.text.x=element_text(angle=0, hjust=0))
ggsave('task_core.pdf', width=8, height=6)
```

## Plot the distinctions between the extend system
```{r}
ggplot(df_within_ext, aes(system, diff)) + 
  geom_point(position=position_jitter(w=0.2),
             size=1, alpha=0.8) +
  geom_crossbar(aes(ymin=mdiff, ymax=mdiff, y=mdiff),
                fatten=2.5, width=0.4) +
  theme_bw() +
  labs(x='System', y='Within - Between Correlation') +
  #coord_cartesian(ylim=c(0, 0.3))# +
  #theme(axis.text.x=element_text(angle=0, hjust=0))
ggsave('task_ext.pdf', width=8, height=6)
```

## Compute bootstrapped CIs

```{r, message=FALSE, warning=FALSE}
get_ci <- function(x, R=100) {
  ci <- bootES(x, R=R)
  return(data.frame(t0=ci$t0, lci=ci$bounds[1], rci=ci$bound[2]))
}

# set seed for reproducibility
set.seed(7)
cis <-
df %>%
  group_by(system) %>%
  do(get_ci(.$diff, R=10000))

cis <- 
df %>%
  group_by(system) %>%
  summarise(within=mean(within), between=mean(between)) %>%
  merge(cis)

cis
```

# Perform LMM model on correlations

```{r}
# disable scientific notation
options(scipen=999)
```
```{r}
df_hpal <- read_csv('hpal_pairwise_corr.csv')
df_task <- read_csv('task_pairwise_corr.csv')

# filter out early visual
df_hpal <-
  df_hpal %>%
  filter(!str_detect(systems, 'early_visual'))
  
df_task <-
  df_task %>%
  filter(!str_detect(systems, 'early_visual'))

# add another label for the distinction core/extended system for hpal
system1 <- 
  str_match(df_hpal$systems, '(.*)\\+')[, 2]
system2 <-
  str_match(df_hpal$systems, '\\+(.*)')[, 2]

system1_core <-
  as.numeric(str_detect(system1, 'core'))
system2_core <-
  as.numeric(str_detect(system2, 'core'))

system_type <- system1_core + system2_core
system_type <- mapvalues(system_type, c(0, 1, 2), c('within_extended', 'between', 'within_core'))
df_hpal$system_type <- system_type

# add another label for the distinction core/extended system for task
system1 <- 
  str_match(df_task$systems, '(.*)\\+')[, 2]
system2 <-
  str_match(df_task$systems, '\\+(.*)')[, 2]

system1_core <-
  as.numeric(str_detect(system1, 'core'))
system2_core <-
  as.numeric(str_detect(system2, 'core'))

system_type <- system1_core + system2_core
system_type <- mapvalues(system_type, c(0, 1, 2), c('within_extended', 'between', 'within_core'))
df_task$system_type <- system_type
```

Now run a glmr model on the individual correlations with a contrast
according to within_core and between, and according to within_core and between
```{r}
require(lme4)
# set up between as the reference level so contrats will be against that
df_hpal$system_type <- factor(df_hpal$system_type, 
                              levels=c('between', 'within_core', 'within_extended'))
contrasts(df_hpal$system_type)

m_hpal <- lmer(corr ~ system_type + (1 | subj), df_hpal)
# set seed for reproducibility and get confidence intervals
set.seed(921)
ci_hpal <- confint.merMod(m_hpal, nsim=10000, method='boot', parallel='multicore', ncpus=8)

# now for task
df_task$system_type <- factor(df_task$system_type, 
                              levels=c('between', 'within_core', 'within_extended'))
contrasts(df_task$system_type)
m_task <- lmer(corr ~ system_type + (1 | subj), df_task)
set.seed(923)
ci_task <- confint.merMod(m_task, nsim=10000, method='boot', 
                          parallel='multicore', ncpus=8)

tidy(m_hpal)
ci_hpal
tidy(m_task)
ci_task
```
```{r}
ci_hpal_ <- data.frame(param=row.names(ci_hpal), ci_hpal)
ci_task_ <- data.frame(param=row.names(ci_task), ci_task)
write_csv(ci_hpal_, 'hpal_model_cis.csv')
write_csv(ci_task_, 'task_model_cis.csv')

write_csv(tidy(m_hpal), 'hpal_model_param.csv')
write_csv(tidy(m_task), 'task_model_param.csv')
```